\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-16 public/paper/pyg4ometry.tex
del comma

\subsection{Tessellation of solids (meshing)}
Creating a uniform three dimensional mesh description of all solids (including Booleans) is exceptionally useful, for visualisation and other algorithms, such as overlap 
detection. For each Geant4 solid instance a triangular tessellated Vertex-Face mesh is generated and cached. This mesh is then used to determine the extent 
of placed instances of geometry (physical volumes) and meshes for CSG-derived solids. CSG mesh calculations are performed using a Binary Space Partitioning 
(BSP) tree technique in pure Python~\cite{pycsg} or the Computational Geometry Algorithms Library (CGAL) surface meshes \cite{cgal:bsmf-sm-20b} in C++. In 
general the CGAL implementation is one to two orders of magnitude faster than the pure Python CSG implementation and must be used for large geometries. 
Triangular meshes based on CSG operations involving curved surfaces often contain large numbers of triangles. Before meshes are visualised or written to disk 
various polygon mesh algorithms  from CGAL \cite{cgal:lty-pmp-20b} can be employed to give the meshes more desirable features.

>>>>

\subsection{Tessellation of solids (meshing)}
Creating a uniform three dimensional mesh description of all solids (including Booleans) is exceptionally useful for visualisation and other algorithms, such as overlap 
detection. For each Geant4 solid instance a triangular tessellated Vertex-Face mesh is generated and cached. This mesh is then used to determine the extent 
of placed instances of geometry (physical volumes) and meshes for CSG-derived solids. CSG mesh calculations are performed using a Binary Space Partitioning 
(BSP) tree technique in pure Python~\cite{pycsg} or the Computational Geometry Algorithms Library (CGAL) surface meshes \cite{cgal:bsmf-sm-20b} in C++. In 
general the CGAL implementation is one to two orders of magnitude faster than the pure Python CSG implementation and must be used for large geometries. 
Triangular meshes based on CSG operations involving curved surfaces often contain large numbers of triangles. Before meshes are visualised or written to disk 
various polygon mesh algorithms  from CGAL \cite{cgal:lty-pmp-20b} can be employed to give the meshes more desirable features.
